---
title: "progress-report-HowIsYourDay"
output: html_document
---

# Lab report #4 - instructions

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday (after Thanksgiving) to polish things.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Lab 4: Scraping (into) the Hall of Fame

```{r}
library("tidyverse")
library("ggplot2")
library("rvest")
```
Need:
1. candidate name
2. year
3. votes
4. percent of vote
5. whether the candidate was inducted

```{r}
hof <- Lahman::HallOfFame

html <- read_html("https://www.baseball-reference.com/awards/hof_2026.shtml")
tables <- html_table(html)

head(tables[[1]], 3)

data <- tables[[1]]
actual_col_names <- data[1, ]
colnames(data) <- actual_col_names
data <- data[-1, ]
head(data, 10)

names <- Lahman::People |> select(playerID, nameFirst, nameLast, nameGiven)

rf_data <- data |> select(Name, Votes, `%vote`) |> mutate(
  yearID = 2026,
  Name = gsub("X-", "", Name),
  `Votes` = as.numeric(`Votes`),
  `%vote` = parse_number(`%vote`),
  `inducted` = (`Votes` >= 319) # notes that 319 votes or more is required for election
)

rf_data |> write_csv("HallOfFame_2026-NH.csv")

rf_data

lahman_2026 <- hof |>
  filter(yearID == 2026)

# join names so that we can compare parsed (rf_data) to lahman_2026
ld_data <- lahman_2026 |> inner_join(names, join_by(playerID)) |> 
  select (nameGiven, votes, yearID, inducted) |>
  mutate(`%vote` = votes/425, inducted = (inducted == "Y")) |>
  rename(Name = nameGiven, Votes = votes)


ld_data 

rf_data |> 
  count(inducted)
ld_data |> 
  count(inducted)

rbind(rf_data, ld_data)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
hof <- Lahman::HallOfFame
hof %>% 
  ggplot(aes(x = yearID, y = votes/needed*100, group=playerID)) +
  geom_hline(yintercept = 100, colour="grey70") + 
  geom_line() +
  geom_point(aes(colour = "inducted"), 
    data = hof %>% filter(inducted=="Y")) +
  xlim(c(2000, 2022)) +
  ylab("Percent of votes")
```
