---
title: "progress-report-srav26-isu"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(dplyr)
library(readr)
library(Lahman)
```

```{r}
tables[[1]] %>% head()
tables[[2]] %>% head()
```

```{r}
data <- tables[[1]]

head(data)
colnames(data)
```

```{r}
data <- tables[[1]]

# Fix column names
colnames(data) <- data[1, ]
data <- data[-1, ]

# Clean dataset
data_clean <- data %>%
  select(Name, Votes, `%vote`)

head(data_clean)
```

```{r}

hof <- HallOfFame

head(hof)
```


```{r}
hof_2026 <- hof %>%
  filter(yearID == 2026)

head(hof_2026)
```

```{r}
hof_clean <- hof_2026 %>%
  select(playerID, yearID, inducted, category)

head(hof_clean)
```
## Observations
The Lahman dataset stores Hall of Fame data differently.
It uses player IDs instead of names and includes whether a player was inducted.
This dataset does not directly match the scraped voting table.

```{r}
hof_clean %>%
  filter(inducted == "Y") %>%
  count()
```

```{r}
library(Lahman)

people <- People

people_clean <- people %>%
  select(playerID, nameFirst, nameLast) %>%
  mutate(Name = paste(nameFirst, nameLast))

hof_names <- hof_clean %>%
  left_join(people_clean, by = "playerID")

head(hof_names)
comparison <- data_clean %>%
  left_join(hof_names, by = "Name")

head(comparison)
```

```{r}
comparison %>%
  filter(inducted == "Y")
```

## Conclusion
The scraping process successfully retrieved Hall of Fame voting data.
However, comparing it with the Lahman dataset was challenging due to differences in data structure and naming conventions.
This shows that data cleaning and standardization are important when combining datasets.


