---
title: "Progress Report - Hall of Fame 2026"
author: "Chaitanya Arravelli"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(dplyr)
library(readr)
library(Lahman)
```

```{r}
url <- "https://www.baseball-reference.com/awards/hof_2026.shtml"
html <- read_html(url)

data <- html %>%
  html_element("#hof_BBWAA") %>%   # THIS targets correct table
  html_table(fill = TRUE)

head(data)

colnames(data)
```

```{r}
data_clean <- data[, c(2, 4, 5)]

colnames(data_clean) <- c("Name", "Votes", "percent_vote")
```

```{r}
data_clean <- data_clean %>%
  filter(Name != "Name") %>%
  mutate(
    Votes = as.numeric(Votes),
    percent_vote = parse_number(as.character(percent_vote)),
    yearID = 2026,
    inducted = ifelse(percent_vote >= 75, "Y", "N")
  )

hof_2026 <- data_clean %>%
  select(Name, yearID, Votes, percent_vote, inducted)

head(hof_2026)

```

```{r}
write_csv(hof_2026, "HallOfFame_2026.csv")
```

Data Source

I scraped Hall of Fame 2026 voting data from Baseball Reference:
https://www.baseball-reference.com/awards/hof_2026.shtml

Data Collection

Using the rvest package, I extracted the Hall of Fame voting table by targeting its HTML id (#hof_BBWAA) to avoid unrelated tables.

Data Cleaning

I kept only the Name, Votes, and percent of votes columns.
I removed repeated header rows, converted Votes to numeric, and used parse_number() to clean percentage values.
I added a yearID column (2026) and created an inducted column where candidates with ≥75% votes are marked "Y".

Final Dataset

The final dataset contains: Name, yearID, Votes, percent_vote, and inducted, and is saved as a CSV file.
